Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-05-10 ch04-lrmhinf/lrmhinf.tex
Remark: quality Hinf estimate
Small diction find

%TODO: The quality of the estimate of the H-infinity norm of Delta is completely unknown. In other words, there is no theoretical guarantee about the error. --> Tom: addresseren. Feitelijk hangt dit samen met de kwaliteit van standaard lpm/lrm, toch?

@@

@@

The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a n accurate estimate of the $\Hinf{}$ norm.
It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\infnorm{\Delta}$ and/or reduce the measurement time four-fold.
Furthermore, the results are validated by a detailed validation measurement.
Ongoing research focuses on extending the technique to \gls{MIMO} systems.

>>>>

@@

\begin{remark}
Since the \gls{LRM} is used to locally estimate the \gls{FRF} based on measurements, this sets a limit on the accuracy of the ensuing estimate of the peak value.
This was treated in \secref{sec:nparam:simulations}.
\end{remark}

@@

The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a n accurate estimate of the $\Hinf{}$ norm.
It is observed that the measurement time is reduced by almost an order of magnitude compared with techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\infnorm{\Delta}$ and/or reduce the measurement time four-fold.
Furthermore, the results are validated by a detailed validation measurement.
Ongoing research focuses on extending the technique to \gls{MIMO} systems.
